Methods for Large Scale Learning to Rank

### 2014-04-07 report/Chapters/CrossBenchmarkComparison.tex
twee smaken Genetic Programming voor ranking!

DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost & \cite{Freund2003} & \cite{Busa-Fekete2013} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} & \cite{Herbrich1999, Joachims2002} & \cite{Busa-Fekete2013, Freno2011, He2010} \\ 

@@

\acs{GP}Rank & \cite{Silva2009} & \cite{Torkestani2012} & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\ 

>>>>

DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost & \cite{Freund2003} & \cite{Busa-Fekete2013, Alcantara2010} \\ 

@@

FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} & \cite{Herbrich1999, Joachims2002} & \cite{Busa-Fekete2013, Freno2011, He2010, Alcantara2010} \\ 

@@

\acs{GP}Rank & \cite{Silva2009} & \cite{Torkestani2012, Alcantara2010} & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\ 
